---
title: "Arabica Coffee Quality Storyboard"
bibliography: CoffeeCitations.bib
output: 
  flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Sidebar {.sidebar}

Preparing the dashboard based on the instructions given at @magallanes_reyes_data_2022, and @aden-buie_flexdashboard_2023.

The GitHub repository this dashboard was constructed with can be found at: https://github.com/JoeVincent0/690Vfinalsubmission

Author: Joseph Vincent

DACSS 690V - Spring 2024

## Column {.tabset .tabset-fade}


### Grow Altitudes

```{r}
readRDS("barplotaltitude.rds")
```


### Total Cup Points Distribution

```{r}
readRDS("cuppointshistogram.rds")
```

### Total Cup Points by Altitude

```{r}
readRDS("violinplotaltitude.rds")
```


### Map of Coffee Lot Origins

```{r}
readRDS("lotsmap.rds")
```


### References 

B., Fatih. “Coffee Quality Data (CQI May-2023),” n.d. https://www.kaggle.com/datasets/fatihb/coffee-quality-data-cqi.

“Coffee Quality Institute,” April 23, 2024. https://www.coffeeinstitute.org/.

Wickham, Hadley. Ggplot2: Elegant Graphics for Data Analysis. 2nd ed. 2016. Use R! Cham: Springer International Publishing : Imprint: Springer, 2016. https://doi.org/10.1007/978-3-319-24277-4.

Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy McGowan, Romain François, Garrett Grolemund, et al. “Welcome to the Tidyverse.” Journal of Open Source Software 4, no. 43 (November 21, 2019): 1686. https://doi.org/10.21105/joss.01686.
